### 2017-09-30 TF-vldb2018/subsec-Ginc.tex

\sstab{(1)} for some unit data update $\delta$ of $\Delta G$, where
(a) $\delta$ is an edge insertion/deletion, $(w_1,w_2)^+/(w_1,w_2)^-$, and $v\in V_{\ball{[w_1,r]}}\cap V_{\ball{[w_2,r]}}$, or
(b) $\delta$ is a node insertion/deletion, $(w,(w,w'))^+$/$(w)^-$, and $v\in V_{\ball{[w,r]}}$; or

>>>>

\sstab{(1)} for some unit data update $\delta$ of $\Delta G$, where
(a) $\delta$ is an edge insertion/deletion, $(w_1,w_2)^+/(w_1,w_2)^-$ and $v$ in  both $\ball{[w_1,r]}$  and $\ball{[w_2,r]}$, or
(b) $\delta$ is a node insertion/deletion, $(w,(w,w'))^+$/$(w)^-$ and $v$ in $\ball{[w,r]}$; or

### 2017-09-30 TF-vldb2018/subsec-Qinc.tex

\eetitle{(2) No edge/node deletions in $\Delta P_{fi}$}.
\incmatch processes updates of the same type together in this case.

\eetitle{(2).i Capacity changes in $\Delta P_{fi}$ or updates on $C$}.
In this case, no computation is needed for maintaining \revise{partial relations for} \affballsx at all,
\ie $M(P_{fi}\oplus\Delta P_{fi}, \ball{}) = M(P_{fi}, \ball{})$.
\warn{Only a capacity check and an inner ball results check in the combination procedure are needed} (to see in Section~\ref{subsubsec-combine}).

@@

%\eetitle{(3) Edge insertions in $\Delta P_{fi}$ only}.
\eetitle{(2).i Edge insertions in $\Delta P_{fi}$}.
In this case, \incmatch calls procedure \patedgeinsert to process edge insertions.
% $|\Delta P_{fi}|$ times.

@@

\stitle{Procedure \patedgeinsert}.
Given $M(P_{fi}, \ball{[v,r]})$ (also represented by $\matchs(\cdot)$), $\ball{[v,r]}$ and an edge insertion $\delta=(u,u')$, \patedgeinsert computes $M(P_{fi}\oplus\delta, \ball{[v,r]})$ {\em incrementally}, as shown in Fig.~\ref{alg-patedgeinsert},
along the same lines as for data incremental graph simulation~\cite{FanWW13-tods}.
\patedgeinsert first finds the directly affected data nodes which need to be removed from $\matchs(\cdot)$ due to the edge insertion to $P_{fi}$,
and pushes them along with the matched pattern nodes into $\kw{RMv}$ (lines 3-8).
It then recursively identifies and removes the nodes in $\matchs(\cdot)$ affected by the previous removed nodes (lines 9-14).
The recursive process is executed by utilizing a stack $\kw{RMv}$.
If there exists a pattern node $u$ with empty $\matchs(u)$, then $\matchs(\cdot)$ is set to $\emptyset$ (line 15).
Finally, \patedgeinsert returns the updated $\matchs(\cdot)$ for $P_{fi}\oplus \delta$ (lines 16-17).
\looseness=-1

\begin{example}
\label{exa-edge-insertion}
Consider case (1)-(b) in Example~\ref{exa-lazyupdate}.
Given $\delta_2 = (\kw{BA},\kw{UD})^+$, and $M(P_{f1}, \ball{}_{\kw{PM_1}})$, which is composed of nodes \kw{PM_1}, \kw{BA_1} and \{\kw{UD_1},\kw{UD_2}\} mapped to nodes \kw{PM}, \kw{BA} and \kw{UD} in $P_{f1}$.
To compute the updated $M(P_{f1}\oplus \delta_2, \ball{}_{\kw{PM_1}})$,
\patedgeinsert removes \kw{UD_2} which is directly affected by $\delta_2$, and finds no other nodes need to be removed.
\end{example}

@@

%\eetitle{(4) Node insertions in $\Delta P_{fi}$ only}.
\eetitle{(2).ii Node insertions in $\Delta P_{fi}$}.
Node insertions are handled in the same way as edge insertions, by extending \patedgeinsert.

Given a node insertion $\delta$ = $(u,(u,u'))^+$, where $u$ is a newly inserted node,
to compute the updated $M(P_{fi}\oplus \delta, \ball{[v,r]})$,
\incmatch firstly computes the set of nodes $\matchs(u)$ in $\ball{[v,r]}$ which have the same label with $u$, and then calls \patedgeinsert($M(P_{fi}, \ball{[v,r]})$, $\ball{[v,r]}$, $(u,u')$) to get the updated result.

@@

Algorithm \incp finally combines the updated partial match relations in \affballsx to get the updated top-$k$ perfect subgraphs $L_{k}(P\oplus \Delta P,G)$ by procedure \comb. Observe that only the balls from \affballsx which match with all pattern fragments of $P\oplus \Delta P$ can enter the combination process.

\stitle{Procedure \comb}. For an \affballx $\ball{[v,r]}$, \comb invokes $\patedgeinsert(\bigcup_{i\in [1, h]}M(P_{fi},\ball{[v,r]}), \ball{[v,r]}, C\oplus \Delta C)$
to compute the maximum match relations of $P\oplus \Delta P$ for $\ball{[v,r]}$ incrementally,
where $\Delta C$ consists of the edge insertions/deletions in $\Delta P$ applied to the cut edges $C$.
It then checks whether the capacity bounds, together with the updates on them, are satisfied.
If so, it constructs the perfect subgraph \wrt the match relations above.
\warn{It then checks the inner balls results together with the capacity bounds} and finally returns the list of top-$k$ perfect subgraphs $L_{k}(P\oplus \Delta P,G)$.

@@

\sstab
(1) For $\ball{[\kw{PM_1},2]}$ and $\ball{[\kw{PM_2},2]}$, as $C\oplus \Delta C=\{(\kw{PM},\kw{SA})\}$,
\comb finds that there is an \kw{SA_i} (resp.\,\kw{PM_j}) connecting to \kw{PM_j} (resp.\,\kw{SA_i}),
and the capacity bounds are satisfied.
\warn{For inner balls, based on above results, \comb finds that no perfect subgraphs reside in $\ball{[\kw{PM_1},1]}$ and $\ball{[\kw{PM_2},1]}$.}
Hence it returns above two perfect subgraphs in two balls.

\sstab
(2) For $\ball{[\kw{BA_3},2]}$, \comb finds no \kw{SA_i} connecting to \kw{PM_j}, and vice versa.
\warn{So no results are in it and its inner balls.}
\end{example}

@@

\begin{figure}[t!]
	%\vspace{-2ex}
	\begin{center}
		{\small
			\myhrule \vspace{-2ex}
			\mat{0ex}{
				\sstab {\sl Input:\/} \= $P$, $h$-fragmentation ${\cal P}_{h}$, $G$, integers $r$ and $k$, $\Delta P$, and\\
				\>auxiliary structures $\tilde{M}(P,G)$, \fb, \bfc and \upl.\\
				{\sl Output:\/} Top-$k$ perfect subgraphs for $P \oplus \Delta P$ in $G$.\\
				\sstab \bcc \hspace{1ex} \= $L_{k}$ := $\emptyset$;\\
				\icc \> \affballsx\ :=  $\identifyaffball({\cal P}_h, \Delta P, \fb, \bfc)$;\\
				\icc \> Sort \affballsx by $\ball{}[\kw{den}]$ in non-ascending order;\\
				\icc \> \For \Each $\ball{[v,r]}$ in \affballsx \Do\quad/* non-ascending order */\\
				\icc \> \hspace{3ex} \= \If $|L_{k}| \geq k$ \And $\ball{[v,r]}[\kw{den}] \leq \density{L_{k}[k]}$ \Then \\
				\icc \>\>\hspace{2ex} \= \bf{Output} $L_{k}[0:k-1]$.\quad/* early-return optimization*/\\
				%/* Running in background after returning top-$k$ results for $\Delta P$ */\\
				\icc \>\>$\incmatch(M(P_{fi},\ball{[v,r]}),\ball{[v,r]}, \Delta P_{fi})$ $(i\in[1,h])$;\\
				\>\> /* runs in the background */\\
				\icc \>\> $S_{G_s} := \comb(\bigcup_{i\in [1, h]}M(P_{fi},\ball{[v,r]}), \ball{[v,r]}, C\oplus \Delta C)$;\\
				\icc \>\> Insert the set of perfect subgraphs in $S_{G_s}$ into $L_{k}$;\\
				\icc \> \Return $L_{k}[0:k-1]$.
				%\icc \>\> \If $|L_{k}| < k$ or $\kw{den}(G_s) > \density{L_{k}[k]}$ \Then\\
				%\icc \>\>\hspace{2ex} \= remove the $k$-th result in $L_{k}$ and insert $G_s$ into $L_{k}$.
				%\icc \hspace{-0.2ex}/*b*\hspace{-0.6ex}/\>\>Update the record of $\ball{[v,r]}$ in \fb;
			}
			\vspace{-2.5ex} \myhrule
		}
	\end{center}
	\vspace{-3ex}
	\caption{Algorithm \incp} \label{alg-optInc}
	\vspace{-4ex}
\end{figure}

>>>>

\eetitle{(2) No edge/node deletions in $\Delta P_{fi}$}.
\incmatch processes updates of the same type together in this case as follows.

\sstab{(i) Capacity changes in $\Delta P_{fi}$ or updates on $C$}.
In this case, no computation is needed for maintaining partial relations for \affballsx at all,
\ie $M(P_{fi}\oplus\Delta P_{fi}, \ball{}) = M(P_{fi}, \ball{})$.
Only a capacity check and an inner ball check in the combination procedure are needed (to see in Section~\ref{subsubsec-combine}).

@@

%\eetitle{(3) Edge insertions in $\Delta P_{fi}$ only}.
\sstab{(ii) Edge insertions in $\Delta P_{fi}$}.
In this case, \incmatch calls procedure \patedgeinsert to process edge insertions.
% $|\Delta P_{fi}|$ times.

@@

\stitle{Procedure \patedgeinsert}.
Given $M(P_{fi}, \ball{[v,r]})$ (also represented by $\matchs(\cdot)$), $\ball{[v,r]}$ and an edge insertion $\delta=(u,u')$, \patedgeinsert computes $M(P_{fi}\oplus\delta, \ball{[v,r]})$ {\em incrementally}, as shown in Fig.~\ref{alg-patedgeinsert},
along the same lines as for data incremental graph simulation~\cite{FanWW13-tods}.
\patedgeinsert first finds the directly affected data nodes that need to be removed from $\matchs(\cdot)$ due to the edge insertion to $P_{fi}$,
and pushes them along with the matched pattern nodes into $\kw{RMv}$ (lines 3-8).
It then recursively identifies and removes the nodes in $\matchs(\cdot)$ affected by the previous removed nodes (lines 9-14).
The recursive process is executed by utilizing a stack $\kw{RMv}$.
If there exists a pattern node $u$ with empty $\matchs(u)$, then $\matchs(\cdot)$ is set to $\emptyset$ (line 15).
Finally, \patedgeinsert returns the updated $\matchs(\cdot)$ for $P_{fi}\oplus \delta$ (lines 16-17).
\looseness=-1

\begin{example}
\label{exa-edge-insertion}
Consider case (1)-(b) in Example~\ref{exa-lazyupdate}.
Given $\delta_2 = (\kw{BA},\kw{UD})^+$, and $M(P_{f1}, \ball{}_{\kw{PM_1}})$, which is composed of nodes \kw{PM_1}, \kw{BA_1} and \{\kw{UD_1},\kw{UD_2}\} mapped to nodes \kw{PM}, \kw{BA} and \kw{UD} in $P_{f1}$.
To compute the updated $M(P_{f1}\oplus \delta_2, \ball{}_{\kw{PM_1}})$,
\patedgeinsert removes \kw{UD_2} that is directly affected by $\delta_2$, and finds no other nodes need to be removed.
\end{example}

@@

%\eetitle{(4) Node insertions in $\Delta P_{fi}$ only}.
\sstab{(iii) Node insertions in $\Delta P_{fi}$}.
Node insertions are handled in the same way as edge insertions, by extending \patedgeinsert.

Given a node insertion $\delta$ = $(u,(u,u'))^+$, where $u$ is a newly inserted node,
to compute the updated $M(P_{fi}\oplus \delta, \ball{[v,r]})$,
\incmatch firstly computes the set of nodes $\matchs(u)$ in $\ball{[v,r]}$ that have the same label with $u$, and then calls \patedgeinsert($M(P_{fi}, \ball{[v,r]})$, $\ball{[v,r]}$, $(u,u')$) to get the updated result.

@@

Algorithm \incp finally combines the updated partial match relations in \affballsx to get the updated top-$k$ perfect subgraphs $L_{k}(P\oplus \Delta P,G)$ by procedure \comb. Observe that only the balls from \affballsx that match with all pattern fragments of $P\oplus \Delta P$ can enter the combination process.

\stitle{Procedure \comb}. For an \affballx $\ball{[v,r]}$, \comb invokes $\patedgeinsert(\bigcup_{i\in [1, h]}M(P_{fi},\ball{[v,r]}), \ball{[v,r]}, C\oplus \Delta C)$
to compute the maximum match relations of $P\oplus \Delta P$ for $\ball{[v,r]}$ incrementally,
where $\Delta C$ consists of the edge insertions/deletions in $\Delta P$ applied to the cut edges $C$.
It then checks whether the capacity bounds, together with the updates on them, are satisfied.
If so, it constructs the perfect subgraph \wrt the match relations above.
It then checks the inner balls together with the capacity bounds, and finally returns the list of top-$k$ perfect subgraphs $L_{k}(P\oplus \Delta P,G)$.

@@

\sstab
(1) For $\ball{[\kw{PM_1},2]}$ and $\ball{[\kw{PM_2},2]}$, as $C\oplus \Delta C=\{(\kw{PM},\kw{SA})\}$,
\comb finds that there is an \kw{SA_i} (resp.\,\kw{PM_j}) connecting to \kw{PM_j} (resp.\,\kw{SA_i}),
and the capacity bounds are satisfied.
For inner balls, based on above results, \comb finds that no perfect subgraphs reside in $\ball{[\kw{PM_1},1]}$ and $\ball{[\kw{PM_2},1]}$.
Hence it returns the above two perfect subgraphs in two balls.

\sstab
(2) For $\ball{[\kw{BA_3},2]}$, \comb finds no \kw{SA_i} connecting to \kw{PM_j}, and vice versa.
Hence, there are no matches found in it and its inner balls.
\end{example}

@@

\begin{figure}[t!]
	%\vspace{-2ex}
	\begin{center}
		{\small
			\myhrule \vspace{-2ex}
			\mat{0ex}{
				\sstab {\sl Input:\/} \= $P$, $h$-fragmentation ${\cal P}_{h}$, $G$, integers $r$ and $k$, $\Delta P$, and\\
				\>auxiliary structures $\tilde{M}(P,G)$, \fb, \bfc and \upl.\\
				{\sl Output:\/} Top-$k$ perfect subgraphs for $P \oplus \Delta P$ in $G$.\\
				\sstab \bcc \hspace{1ex} \= $L_{k}$ := $\emptyset$;\\
				\icc \> \affballsx\ :=  $\identifyaffball({\cal P}_h, \Delta P, \fb, \bfc)$;\\
				\icc \> Sort \affballsx by $\ball{}[\kw{den}]$ in non-ascending order;\\
				\icc \> \For \Each $\ball{[v,r]}$ in \affballsx \Do\quad/* non-ascending order */\\
				\icc \> \hspace{3ex} \= \If $|L_{k}| \geq k$ \And $\ball{[v,r]}[\kw{den}] \leq \density{L_{k}[k]}$ \Then \\
				\icc \>\>\hspace{2ex} \= \bf{Output} $L_{k}[0:k-1]$. /* early-return optimization*/\\
				%/* Running in background after returning top-$k$ results for $\Delta P$ */\\
				\icc \>\>$\incmatch(M(P_{fi},\ball{[v,r]}),\ball{[v,r]}, \Delta P_{fi})$ $(i\in[1,h])$;\\
				\>\> /* runs in the background */\\
				\icc \>\> $S_{G_s} := \comb(\bigcup_{i\in [1, h]}M(P_{fi},\ball{[v,r]}), \ball{[v,r]}, C\oplus \Delta C)$;\\
				\icc \>\> Insert the set of perfect subgraphs in $S_{G_s}$ into $L_{k}$;\\
				\icc \> \Return $L_{k}[0:k-1]$.
				%\icc \>\> \If $|L_{k}| < k$ or $\kw{den}(G_s) > \density{L_{k}[k]}$ \Then\\
				%\icc \>\>\hspace{2ex} \= remove the $k$-th result in $L_{k}$ and insert $G_s$ into $L_{k}$.
				%\icc \hspace{-0.2ex}/*b*\hspace{-0.6ex}/\>\>Update the record of $\ball{[v,r]}$ in \fb;
			}
			\vspace{-2.5ex} \myhrule
		}
	\end{center}
	\vspace{-3ex}
	\caption{Algorithm \incp} \label{alg-optInc}
	\vspace{-4ex}
\end{figure}
